---
title: "Indiana COVID animation"
author: "Andy Borst"
date: "10/19/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mongolite)
library(dplyr)
library(lubridate)
library(readr)
library(tibble)
library(RSocrata)
library(ggplot2)
library(gganimate)
library(gifski)
```

MongoDB and R together workshop.
1. Install MongoDB server using MongoDB documentation and not old packages in repo
  + Version 4.4.1
  + systemctl start mongod
  + mongo to enter shell (db.help())
  + url = "mongodb://127.0.0.1:27017"
2. Connect and create MongoDB collection from online data source 
3. Import the data back from MongoDB
4. Grab new data and append to the collection
5. Use gganimate to publish shiny horizontal bar chart 


```{r , echo=TRUE}
covid <- read.socrata("https://data.cdc.gov/api/views/9mfq-cb36/rows.csv")
m <- mongo(db = "covid", collection = "socrata_covid") 
#create collection 
m$insert(covid)

#returns all records
covid <- m$find()
#returns n records
df <- m$find('{}', limit = 10)
#example of filtered query with selected fields
df <- m$find(query = '{"date": "2020-10-17"}')

#unique values of field
m$distinct("date")
m$distinct("_id")

m$info()

#commands 
m$run(command = '{"listCollections" : 1}') 
m$run(command = '{"db" : 1}') 

admin <- mongo(db = "admin")
admin$run('{"listDatabases": 1}')
admin$disconnect()

#to create a collection use the collection name in connection
m <- mongo(db = "covid", collection = "indiana" ) 
m$insert(Indiana_covid)
m$run('{"count":"indiana"}')



```

```{r}
c <- covid %>%
    mutate(Month = month(submission_date)) %>% 
    select(state, Month, new_death) %>% 
    group_by(state, Month) %>%
    summarise(Deaths = sum(new_death)) %>% 
    ungroup()

c_percent_increase <- c %>%
  group_by(state) %>% 
  mutate(Percent = Deaths / lag(Deaths)) %>%
  filter(is.finite(Percent)) %>% 
  ungroup() 


c_slice <-  c_percent_increase %>% 
  group_by(Month) %>%
  # The * 1 makes it possible to have non-integer ranks while sliding
  mutate(rank = rank(-Percent),
         Value_rel = Percent/Percent[rank==1],
         Value_lbl = paste0(" ",round(Percent/1e9))) %>%
  group_by(state) %>% 
  filter(rank <=10) %>%
  ungroup()
  

p <- ggplot(c_slice, aes(rank, group = state, 
                fill = as.factor(state), color = as.factor(state))) +
  geom_tile(aes(y = Percent/2,
                height = Percent,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(state, " ")), vjust = 0.2, hjust = 1) +
  geom_text(aes(y=Percent,label = Value_lbl, hjust=0)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=25, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"))

anim = p + transition_states(Month, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  

animate(anim, 200, fps = 20,  width = 1200, height = 1000, 
        renderer = gifski_renderer("gganim.gif"))
```

